quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-21 paper-quollr.tex
Fixed the .bib issue

\begin{verbatim}
glance(
  model_object = scurve_model_obj,
  highd_data = scurve
  )
\end{verbatim}

@@

\begin{verbatim}
model_error <- augment(
  model_object = scurve_model_obj,
  highd_data = scurve
  )

>>>>

\begin{verbatim}
glance(
  x = scurve_model_obj,
  highd_data = scurve
  )
\end{verbatim}

@@

\begin{verbatim}
model_error <- augment(
  x = scurve_model_obj,
  highd_data = scurve
  )
